---
title: "Untitled"
output:
  pdf_document: default
  html_document: default
---

---
title: "Week9_Markdown"
output:
  pdf_document: default
  html_document: default
---

This is an Rmarkdown document. I can type whatever I want.

**This is bold**

*This is italic*

### This will make the font bigger
##This will make it slightly smaller

Ctrl-Alt-I shortcut to add code

```{r}
library(tidyverse)
glimpse(storms)

library(viridis) #do not install packages in R Markdown files, install in console

ggplot(data=storms)+
  geom_jitter(aes(x= as.factor(month), y=pressure, fill=wind), pch=21, alpha= .05)+
  scale_fill_viridis_c()+
  theme_bw()+
  labs(title = "Hurricane Pressure v  Month", subtitle ="with Max Wind Speed", x="Month")
```

Everything that would normally pop-up in our console will show up in our html document



```{r, warning=FALSE, message=FALSE}
suppressPackageStartupMessages(library(tidyverse))
glimpse(storms)

library(viridis) #do not install packages in R Markdown files, install in console

ggplot(data=storms)+
  geom_jitter(aes(x= as.factor(month), y=pressure, fill=wind), pch=21, alpha= .05)+
  scale_fill_viridis_c()+
  theme_bw()+
  labs(title = "Hurricane Pressure v  Month", subtitle ="with Max Wind Speed", x="Month")


```

Writing our equations in Rmarkdown:

If you want to write an equation, you put a $ on either side of it.

$\sum_{i=y}^n x_i$

```{r}
library(knitr)

kable(head(storms), caption="Table using Kable")

htmlTable::htmlTable(head(storms))

#make an interactive table

DT::datatable(storms)

```


```{r}
library(plotly)

ggplotly(
  ggplot(data=storms)+
  geom_jitter(aes(x= as.factor(month), y=pressure, fill=wind), pch=21, alpha= .05)+
  scale_fill_viridis_c()+
  theme_bw()+
  labs(title = "Hurricane Pressure v  Month", subtitle ="with Max Wind Speed", x="Month")
)

#Plotly allows you to look at different layers of plot, zoom in/out, etc.

```

```{r}
library(leaflet)  #produces interactive maps

# filter data down 
storms <- filter(storms, year > 2006)

# set up a color palette:
pal <- colorNumeric(
  palette = "RdYlBu",
  domain = storms$wind)

# make a map
m <- leaflet() %>% addTiles() %>% 
  addProviderTiles("Esri.WorldImagery", group = "ESRI Aerial") %>%
  addProviderTiles("Esri.WorldTopoMap", group = "Topo") %>%
  
# proposed sites
  addCircleMarkers(data=storms, group="Storms",
                   lng= ~long, lat= ~lat,
                   stroke=TRUE, weight=0.6, radius=4,
                   fillOpacity = 0.5, color=~pal(wind)) %>%
  
  # add controls for basemaps and data
  addLayersControl(
    baseGroups = c("ESRI Aerial", "Topo"),
    overlayGroups = c("Storms"),
    options = layersControlOptions(collapsed = T))

m
```












